DraftOne

### 2016-06-10 DraftOne.Rmd
Creating seasonal_outcome function

@@

        if(trend=="constant"){
          if(x_type == "binary"){
            x <- binary_exposure(n=n, ...)
          }
          else if(x_type == "continuous"){
            x <- continuous_exposure(n=n, ...)
          }
          exp_base_y <- constant_baseline(n=n, ...)
          df <- full_join(x, exp_base_y, by="date") %>% mutate(exp_y = 
                 exp(log(exp_base_y)+log(rr)*x))
          df$y <- sapply(df$exp_y, FUN = function(x) rpois(1,x))
        }
        else if(trend != "constant"){
          if(x_type == "binary"){
            x <- season_binexp(n = n,...)
          }
          else if(x_type == "continuous"){
            x <- season_contexp(n = n, ...)
          }

        }
  return(df)
}

@@

        if(x_type == "binary" & trend == "constant"){
                x <- binary_exposure(n = n, ...)
                exp_base_y <- constant_baseline(n=n, ...)
                df <- full_join(x, exp_base_y, by="date")
                df <- mutate(df, exp_y=exp(log(exp_base_y)+log(rr)*x))
                df$y <- sapply(df$exp_y, FUN = function(x) rpois(1,x))
        } else if(x_type == "continuous" & trend=="constant"){
                x <- continuous_exposure(n = n, ...)
                exp_base_y <- constant_baseline(n=n, ...)
                df <- full_join(x, exp_base_y, by="date")
                df <- mutate(df, exp_y=exp(log(exp_base_y)+log(rr)*x))
                df$y <- sapply(df$exp_y, FUN=function(x) rpois(1,x))

@@

}
```

>>>>

```{r}
#Seasonal baseline
seasonal_baseline <- function(n, lambda, trend, start.date="2000-01-01", ...){
  start.date <- as.Date(start.date)
  date <- seq(from = start.date, by=1, length.out=n)
  t <- calc_t(n=n, ...)
  exp_base_y <- lambda*t
  df <- data.frame(date=date, exp_base_y=exp_base_y)
  return(df)
}
```

@@

        if(trend=="constant"){
          if(x_type == "binary"){
            x <- binary_exposure(n=n, ...)
          }
          else if(x_type == "continuous"){
            x <- continuous_exposure(n=n, ...)
          }
          exp_base_y <- constant_baseline(n=n, ...)
          df <- full_join(x, exp_base_y, by="date") %>% mutate(exp_y = 
                 exp(log(exp_base_y)+log(rr)*x))
          df$y <- sapply(df$exp_y, FUN = function(x) rpois(1,x))
        }
        else if(trend != "constant"){
          t <- calc_t(n=n, ...)
          if(x_type == "binary"){
            x <- season_binexp(n = n,...)
          }
          else if(x_type == "continuous"){
            x <- season_contexp(n = n, ...)
          }
          exp_base_y <- 
        }
  return(df)
}

@@

@@

```
